Workflow

### 2014-11-18 Workflow/Workflow.Rmd
Noted that the script now connects to dahl. Used to connect to fs1, but there were times when new files would not propagate across the cluster before the download request was made. This caused some confusion.
Added notes about the r-versions script.

### Create the batch script
* Create the file `Scripts/<Source>_batch.bash` file.
    + It is probably best to modify an existing `<Source>_batch.bash` file.      
    + Be sure to edit the `$SRC` variable.
    + Distribute the work over the nodes in a way that makes sense.
* Push the `<Source>_batch.bash` file to GitHub.
* On `acc`, pull from GitHub.

@@

### Download post-processed results to local machine
* From a local machine, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source> -d`, where `<user>` is 
a username on `dahl`, `<Source>` is the data source of interest, and `-d` (debug) will 
show the files to be transferred to the local machine, without actually transferring them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source>` to download the files.
* The files are downloaded to the `data_postprocessed` directory on the local machine.
* Use the function `loadPostProcessedData` in the `EconData` package to load the downloaded data into
the environment.

>>>>

### Create the batch script
* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`.
* Create the file `Scripts/<Source>_batch.bash` file.
    + It is probably best to modify an existing `<Source>_batch.bash` file.      
    + Be sure to edit the `$SRC` variable.
    + Distribute the work over the nodes in a way that makes sense.
    + Avoid non-working nodes or nodes that have an out-of-date version of `R` as revealed by `r-versions`.
* Push the `<Source>_batch.bash` file to GitHub.
* On `acc`, pull from GitHub.

@@

### Download post-processed results to local machine
* From a local machine, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source> -d`, where `<user>` is 
a username on `dahl`, `<Source>` is the data source of interest, and `-d` (debug) will 
show the files to be transferred to the local machine, without actually transferring them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source>` to download the files.
* The files are downloaded to the `data_postprocessed` directory on the local machine.
* Use the function `loadPostProcessedData` in the `EconData` package to load the downloaded data into
the environment. 
* The `DownloadPostProcessed.bash` script connects to `dahl.calvin.edu` (`node-00`). 
That choice was made to minimize the risk that a file won't prpogate across the cluster 
file system prior to the download request.
